\documentclass[notitlepage]{article}

% page geometry --- easiest way to do this is to use the geometry package
\usepackage{geometry}
\geometry{width=5in, textheight=7.75in, headsep=0.25in, footskip=.5in, 
          twosideshift=0pt}

\usepackage[plainpages=false,linktocpage,colorlinks,linkcolor=red,pagecolor=red,urlcolor=red,pageanchor,bookmarks,nativepdf,hyperindex,pagebackref]{hyperref}

%\input{page}

\begin{document}

\thispagestyle{empty}

\noindent
For Addison-Wesley:


Executive Editor: Carter Shanklin


Editorial Assistant: Rachel Beavers


Manufacturing Coordinator: Judy Sullivan


Copyeditor: Katrina H. Avery


Proofreader: Cynthia Benn


Cover Designers: Scott Klemmer and Michael Legrand

\vspace{3ex}
\noindent
Access the latest information about this book at 
\href{http://www.modelsofcomputation.org}{{\em http://www.modelsofcomputation.org}}

\vspace{3ex}
\noindent
The programs and applications presented in this book have been included for
their instructional value.  They have been tested with care, but are not
guaranteed for any particular purpose. No warranties or representations are
given by the author nor does he accept any liabilities with respect to the
programs or applications.

\vspace{3ex}
\begin{verbatim}
Library of Congress Cataloging-in-Publications Data

Savage, John E., 1939-
   Models of computation : exploring the power of computing / John Savage
      p.  cm.

   Includes bibliographical references and index.
   ISBN 0-201-89539-0
 1. Computer science. 2. System analysis. I. Title
 QA76.S333  1998                                               9724307
 004---dc21                                                      CIP
\end{verbatim}

\vspace{1ex}
\noindent
Copyright {$\copyright$}1998, John E. Savage, Providence, RI. 

\vspace{2ex}
\noindent
This work is licensed under a Creative Commons
Attribution-Noncommercial-No Derivative Works 3.0 United States
License and released electronically. 
\break
(See \href{http://creativecommons.org/licenses/by-nc-nd/3.0/us/}
{{\em http://creativecommons.org/licenses/by-nc-nd/3.0/us/}})


\vspace{2ex}
\noindent
To seek permission for the commercial use, copying, and/or distribution of the
material in this publication, please contact the author at
John\_Savage@brown.edu.

\vspace{2ex}
\noindent
This document was published as a book in 1998 by Addison-Wesley.
Addison-Wesley, now a division of Pearson Publishing Group, has returned all
rights to the document to the author.

\vspace{2ex}
\noindent
This document was published as a book from 2002 until 2007 by XanEdu
OriginalWorks, a division of ProQuest Information \& Learning, Ann
Arbor, MI 48106, 800-218-5971.

\vspace{2ex}
\noindent
This document was released in electronic form on July 23, 2008.

\end{document}
\break
